Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/1_introduction.tex
modify intro
Updated 1_intro.tex, and 2_motivation.tex

In this paper, we propose cloud-based burst buffers. The cloud-based burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
We also model the cloud-based burst buffers to optimize  configurations of the cloud-based burst buffers according to dynamically changing environments
\kento{Do you think this sentence is resonable to describe your model ?}.
\kento{please summirize the evaluation resutls here.}
%  architecture that uses multiple nodes in each system as an I/O nodes 
%to improve I/O throughput concurrent data transferring, and an I/O burst buffer model 
%that uses to switch between I/O burst buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
%Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
%but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contributions can be summrized as following:
\begin{itemize}
	\item A cloud-based burst buffer for increasing data transfer throughput between two systems;
	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and AMAZON EC2.
\end{itemize}
%2
The rest of this paper is organized as follows. 
In Section \ref{sec:motivation}, we clarify the motivation and the background.
We introduce an overview of the I/O bursting buffer architecture in Section \ref{sec:burst_buffer}, 
and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
In Section \ref{sec:evaluation}, we present our experimental results based of our perfomrance models. %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

>>>>

In this paper, we propose I/O burst buffers. The I/O burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
We also model the I/O burst buffers to optimize  configurations of the I/O burst buffers according to dynamically changing environments
\kento{Do you think this sentence is resonable to describe your model ?}.
According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well sa reduce 2-12 times of cost.
\kento{please summirize the evaluation resutls here.}
%  architecture that uses multiple nodes in each system as an I/O nodes 
%to improve I/O throughput concurrent data transferring, and an I/O burst buffer model 
%that uses to switch between I/O burst buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
%Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
%but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contributions can be summrized as following:
\begin{itemize}
	\item A I/O burst buffer for increasing data transfer throughput between two systems;
	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and AMAZON EC2.
\end{itemize}
%2
The rest of this paper is organized as follows. 
In Section \ref{sec:motivation}, we clarify the motivation and the background.
We introduce an overview of the I/O bursting buffer architecture in Section \ref{sec:burst_buffer}, 
and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
In Section \ref{sec:evaluation}, we present our experimental results based of our perfomrance models. %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

### 2014-07-01 paper/src/2_motivation.tex
Updated 1_intro.tex, and 2_motivation.tex

                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)

@@

To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

>>>>

                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)

@@

To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele
